PM Mungbean meta-analysis

### 2020-12-16 02_Preliminary_analysis.Rmd
Add standard error to table

```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.),
             minimum_yield = min(grain_yield.t.ha.),
             maximum_yield = max(grain_yield.t.ha.),
             yield_stdev = sd(grain_yield.t.ha.)) %>%
   kable(align = 'c',
   caption = "Average yield statistics for no spray contol plots"
)

>>>>

```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.),
             minimum_yield = min(grain_yield.t.ha.),
             maximum_yield = max(grain_yield.t.ha.),
             yield_stdev = sd(grain_yield.t.ha.),
             yield_SE = sd(grain_yield.t.ha.)/
                              sqrt(n())) %>%
   kable(align = 'c',
   caption = "Average yield statistics for no spray contol plots"
)
